---
title: "R Notebook"
output: html_notebook
---

```{r}
is_leap_year <- function(year){
  
  if(year %% 100 == 0){
    if(year %% 400 == 0){
      return(TRUE)
    } else {
      return(FALSE)
    }
  }
  if(year %% 4 == 0){
    return(TRUE)
  } else {
    return(FALSE)
  }
}
```

testing if year is divisible by 100 and 400 (special cases of leap year), if 
TRUE can be proven to be a leap year at this point and if not can be disproven
i.e return FALSE

special cases from first section doesn't pass into second section 

next if else testing if year is divisible by 4, if so leap year is TRUE, if not 
FALSE

###testthat package
```{r}
library(testthat)
```
expect_equal(): checking that obects give the answers we expect
expect_error(): checking that the code throws an error

```{r}
a <- 10
expect_equal(a, 10)
```
```{r}
expect_equal(a, 11)
```

```{r}
test_that("Real leap year return TRUE", {
  expect_equal(is_leap_year(2020), TRUE)
  expect_equal(is_leap_year(2000), TRUE)
})
```


```{r}
test_that("Character input returns an error", {
  expect_error(is_leap_year("year"))
})
```
test name - "character input returns an error"

expectation is that there will be an error and test will be passed

this test will run "year" through the function is_leap_year and will return an error as the function cannot process character inputs, as the test is expecting an error the test will be passed

```{r}
test_that("Non-numeric input rturns an error", {
  expect_error(is_leap_year("year"))
  expect_error(is_leap_year(TRUE))
})
```

```{r}
is_leap_year <- function(year){
  
#add in condition for non numeric data 
  if(!is.numeric(year)){
    stop("Non-numeric input :(")
  }
  if(year %% 100 == 0){
    if(year %% 400 == 0){
      return(TRUE)
    } else {
      return(FALSE)
    }
  }
  if(year %% 4 == 0){
    return(TRUE)
  } else {
    return(FALSE)
  }
}
```

#re-test with non-nuneric condition added
```{r}
test_that("Non-numeric input returns an error", {
  expect_error(is_leap_year("year"))
  expect_error(is_leap_year(TRUE))
})
```

```{r}
test_that("Non leap year return FALSE", {
  expect_equal(is_leap_year(2017), FALSE)
  expect_equal(is_leap_year(1900), FALSE)
})
```

