---
title: "R Notebook"
output: html_notebook
---
Distributions: a way of communicating how often something occurs (frequency distribution) / how likely it is to occur (probability distribution)

```{r}
library(tidyverse)
source("prob.R")
```
```{r}
tosscoin(1) %>% 
  mutate(p = 1 / n())
```
# Uniform distribution
```{r}
s_three_coins_labelled <- tosscoin(3) %>% 
  mutate(outcome = str_c(toss1, toss2, toss3, sep = ""),
         p = 1 / n())
  
ggplot(s_three_coins_labelled)+
  aes(x = outcome,
      y = p)+
  geom_col()
```

# Non uniform distribution - prob of 0 heads, 1 heads, 2 heads, 3 heads
```{r}
s_three_coins_labelled %>% 
  mutate(n_heads = str_count(outcome, "H")) %>% 
  group_by(n_heads) %>% 
  summarise(p = sum(p)) %>% 
  ggplot()+
  aes(n_heads, p)+
  geom_col()
```

##Measures of centrality (mean, median, mode) - averages
```{r}
library(janitor)
library(lubridate)
```
```{r}
air_con_sales <- read_csv("data/AirConSales.csv")

air_con_clean <- air_con_sales %>% 
  clean_names() %>% 
  mutate(date = mdy(date))
```

#how often is it to sell a certain number of units? i.e. 3
```{r}
sales_freqs <- air_con_clean %>% 
  tabyl(units_sold)
```
```{r}
sales_freqs %>% 
  ggplot()+
  aes(units_sold, percent)+
  geom_col()
```

#Mean - highly influenced by extreme values
```{r}
air_con_clean %>% 
  summarise(mean_daily_sales = mean(units_sold))
```
#Median - middle value in an ordered sequence
```{r}
air_con_clean %>% 
  summarise(mean_daily_sales = mean(units_sold),
            median = median(units_sold))
```
#Mode - most commonly occuring value
```{r}
get_mode <- function(data){

  tabled_data <- table(data)
  table_names <- names(tabled_data)
  
  return( table_names[tabled_data == max(tabled_data)] )
  
}

air_con_clean %>% 
  summarise(mean_daily_sales = mean(units_sold),
            median = median(units_sold),
            mode = get_mode(units_sold))
```
#Distribution shapes (modality)
>one mode: unimodal
>two modes: bimodal

#Skweness (the assymetry of a distribution)
>left skewed (tail of distribution points left) - mean < median < mode
>right skewed (tail points right) - mode < median < mean
>symmetric

```{r}
library(e1071)
```

quanitfying a skew: < 0.5 fairly symmetric
                      0.5 - 1.0 moderately skewed
                    > 1.0 highly skewed
                    
                    negative - left skew
                    positive - right skew
                    
```{r}
air_con_clean %>% 
  summarise(skew = skewness(units_sold, type = 1))
```



