---
title: "R Notebook"
output: html_notebook
---
```{r}
s_four_coins <- tosscoin(4)
```
#probability of 2 head being thrown 
```{r}
s_four_coins <- s_four_coins %>% 
  mutate(num_heads = rowSums(. == "H"))

s_at_least_2_heads <- s_four_coins %>% 
  filter(num_heads >= 2)

prob_two_heads <- nrow(s_at_least_2_heads) / nrow(s_four_coins) #probability

1 - prob_two_heads # compliment
```

## `AND` combinations 
s: {1, 2, 3, 4, 5, 6}
event A: {1, 2, 3, 4} 
event B: {3, 4, 5, 6}  
#both can only be satisifed by rolling a 3 or 4 with one throw
```{r}
rolldie(1) %>% 
  filter(X1 %in% 3:4)
```
#probability of rolling at least 1 head and one tail, from 4 roll function
```{r}
s_four_coins %>% 
  mutate(num_tails = rowSums(. == "T")) %>% 
  filter(num_heads >= 1, num_tails >= 1) %>% 
  summarise(probability = n()/nrow(s_four_coins))
```
## Mutually exclusive events

>with four coin toss, probability of tossing at least 3 heads and at least 2 tails (throwing 3 heads excludes 2 tails, with 4 coins)

## OR combintaion

> union
event A: roll even number {2, 4, 6}
event B: roll one of {4,5}

```{r}
s_two_dice <- rolldie(2)

s_two_dice %>% 
  filter(X2 %% 2 == 0| X2 == 5) %>% 
  summarise(n() / nrow(s_two_dice))
```
##Task

#first die even
```{r}
s_two_dice %>% 
  filter(X1 %%2 == 0) %>% 
  summarise(n() / nrow(s_two_dice))
```
#second die 5
```{r}
s_two_dice %>% 
  filter(X2 == 5) %>% 
  summarise(n() / nrow(s_two_dice))
```



#first die even and second die 5
```{r}
s_two_dice %>% 
  filter(X1 %%2 == 0, X2 == 5) %>% 
  summarise(n() / nrow(s_two_dice))
```

# first die even or second die 5
```{r}
s_two_dice %>% 
  filter(X1%%2 == 0 | X2 == 5) %>% 
  summarise(n() / nrow(s_two_dice))

0.5 + 0.16666667 - 0.083333 # probability of x1 = even + probability of x2 = 5 - intersect (first die even and second die 5 as satisfies both condiitons)
```

