---
title: "R Notebook"
output: html_notebook
---
## Single step experiments

$$
prob(event) = num(event_outcomes) / num(all_outcomes)
$$
```{r}
s <- rolldie(2)

total_seven <- s %>% 
  filter(X1 + X2 == 7)

nrow(total_seven) / nrow(s)
```

## Multiple step experiments

step 1: rolling a dice - 6 possible outcomes
step 2 tossing a coin - 2 possible outcomes
6*2 = 12 possible outcomes

p(heads) = 1/2
p(6) = 1/6
1/2 * 1/6 = 1/12 probability of 2 step experiment

```{r}
s_die <- rolldie(1)
s_coin <- tosscoin(1)

s_total <- merge(s_coin, s_die)

head_six <- s_total %>% 
  filter(toss1 == "H", X1 == 6)

nrow(head_six)/nrow(s_total)
```

## Permutations and combinations

permutation <- An arrangement of outcomes which the order matters (padlock code)

combination <- An arrangement of outcomes which the order does not matter (lottery ticket)

```{r}
v <- 2:5

fact <- function(n,r){
  factorial(n)/factorial(n-r)
}

fact(4,4)
fact(10, 4)
```


```{r}
library(gtools)
```
```{r}
#example
nrow(permutations(4, 4, repeats.allowed = T))
```
#how many permutations of 10 possible employees to fill 3 positions??
```{r}
employees <- c("Alice", "Bob", "Carole", "David", "Elaine", "Fred", "Gabra", "Hua", "Inigo", "Hugo")

seniors <- as_tibble(permutations(n = 10, r=3, v = employees, repeats.allowed = F))

 seniors <- seniors %>% 
  rename(CEO = V1, CTO = V2, COO = V3)
```
# Probability of alice being selecetd as CEO and John as CTO, if selection is again at random 
```{r}
seniors %>% 
  filter(CEO == "Alice", CTO == "Bob")

8/720 # could be done using nrow after assigning new variable
```

## Combinations
```{r}
num_draws <- choose(50, 6) 

options(scipen = 99)
1 / num_draws
```

# 5 icecream flavours and a bowl that can hold three scoops. How many different variations in bowls of ice cream can I have assuming:
#Each scoop must be a different flavour
#I can repeat flavours if I wish?

```{r}
flavours <- c("vanilla", "chocolate", "raspberry", "strawberry", "pistachio")

bowl_repeats <- combinations(n = 5, r = 3, repeats.allowed = T) %>% 
nrow()

bowl_no_repeats <- combinations(n = 5, r = 3, repeats.allowed = F) %>% 
nrow()
```



