---
title: "R Notebook"
output: html_notebook
---
```{r}
single <- 'this is a single string'
double <- "this is a double string"
```

```{r}
library(tidyverse)
```

```{r}
employees <- tibble(
  first_name = c("Sally", "steven", "Mary", "John"),
  last_name = c("Smith", "hasTings", "Milne", "Davidson"),
  postcode = c("EH10 6GH", "EH3 7HL", "G1 7FR", NA), 
  location = c(" ", "Edinburgh", "", "Stirling")
)

employees
```
```{r}
employees %>% 
  group_by(location) %>% 
  summarise(n())
```

```{r}
mary_location <- employees %>% 
  filter(first_name == "Mary") %>% 
  select(location) %>% 
  pull()

sally_location <- employees %>% 
  filter(first_name == "Sally") %>% 
  select(location) %>% 
  pull()
``` 

```{r}
mary_location == sally_location
```

```{r}
employees %>% 
  summarise(nchar(location))
```
```{r}
str_c("This", "is", "some", "text", sep = " ")
```

```{r}
employees %>% 
  mutate(full_name = paste(first_name, last_name, sep = " "),
         .after = last_name)
```
```{r}
pangram <- "The quick brown fox jumps over the lazy dog"
```

```{r}
pangram %>% 
  str_to_upper()
```

```{r}
pangram %>% 
  str_to_lower()
```

```{r}
pangram %>% 
  str_to_title()
```
```{r}
pangram %>% 
  str_to_sentence()
```

```{r}
employees %>% 
  select(first_name, last_name) %>% 
  mutate(first_name_fix = str_to_title(first_name),
         last_name_fix = str_to_title(last_name))
```
```{r}
unbroken_string <- "We're going to break up this string."
```

```{r}
unbroken_string %>% 
  str_split(" ") %>% 
  flatten_chr()
```

```{r}
employees %>% 
  mutate(new_postcode = str_split(postcode, " ")) %>% 
  unnest(new_postcode)
```
```{r}
employees %>% 
  separate_rows(postcode, sep = " ")
```
```{r}
employees %>% 
  separate(postcode, c("postcode_outer", "postcode_inner"), " ")
```

#Task - 10 mins
#Concatenate the strings "Manipulating" "strings" "is" "fun!"
#Capitalise the result and save it in a new variable
#Split the formatted string into individual characters

```{r}
maniplutaing_strings <- "Manipulating strings is fun!"
```

```{r}
capitalised_strings <- str_to_upper(maniplutaing_strings) %>% 
  str_split("") %>% 
flatten_chr()
```


```{r}
full_string <- "Let's grab a substring from this!"
```

```{r}
full_string %>% 
  str_sub(start = 6)
```

```{r}
full_string %>% 
  str_sub(-5, -1)
```
```{r}
employees %>% 
  mutate(postcode_inner = str_sub(postcode, -3), 
         postcode_outer = str_sub(postcode, 1, -4))
```
```{r}
string <- "We're going to replace some words."
```
```{r}
str_sub(string, 1, 22) <- "I've changed"
```

```{r}
string
```

```{r}
numbers <- 1233456.789
```

```{r}
numbers %>% 
  format(nsmall = 1, decimal.mark = ",")
```

```{r}
numbers %>% 
  format(big.mark = ",", big.interval = 3)
```
#Upcase the text in the playlist_name column. Overwrite the existing column to store the result.

#Lowcase the text in the track_artist column. Store the result in a new column called track_artist_lowcase.

#Take the first 5 characters of the playlist_id column, and save it in a new column called playlist_start.

#Take the first 4 characters of the track_album_release_date column and save it in a new column called year.


#What else can you do to this dataset to practice? Can you work with the numbers? This is open ended - have fun!


```{r}
spotify <- read_csv("data/spotify_sample.csv")
```
```{r}
spotify %>% 
  mutate(playlist_name = str_to_upper(playlist_name))
```
```{r}
spotify %>% 
  mutate(track_artist_lower = str_to_lower(track_artist))
```
```{r}
spotify %>% 
  mutate(playlist_start = str_sub(playlist_id, 1, 5))
```
```{r}
spotify %>% 
  mutate(year = str_sub(track_album_release_date, 1, 4))
```
