---
title: "R Notebook"
output: html_notebook
---

```{r}
mortgage_data_logreg_model <- glm(accepted ~ tu_score,
                                  data = mortgage_data,
                                  family = binomial(link = "logit"))

summary(mortgage_data_logreg_model)
```
probability of acceptance = 1/ 1 + e^(-4.6+0.01*tu_score)

as tu_score increases by 1, probability increases the log odds by 0.008

```{r}
library(modelr)

#0-710 tu_scores
#map a prediction of acceptance for each credit score

log_predictions <- tibble(
  tu_score = seq(0, 710, 1)) %>% 
  add_predictions(mortgage_data_logreg_model,
                  type = "response")

ggplot(mortgage_data)+
  geom_jitter(aes(x = tu_score,
                  y = as.numeric(accepted)), alpha = 0.5, height = 0.1, wodth = 0.1)+
  geom_line(data = log_predictions, aes(x = tu_score, y = pred), col = "red")+
  labs(y  = "estimated probability accepted")

#can use our preicitons by filtering prediciton table 
log_predictions %>% 
  filter(tu_score == 600)
```
how do our odds of getting accpeted change as we increase tu_score?

base on:
  - baseline odds (tu_score = 594)
  - odds above baseline (tu_score = 594 + 50)
  
```{r}
odds_change <- function(b1, change){
  exp(b1 * change)
}

odds_change(0.008475, 50)
```

a 50 unit increase in tu_score leads to odds increasing by a factor of 1.53

###categorical predictors
```{r}
mortgage_model_2_terms <- 
  glm(accepted ~ tu_score + employed,
      family = binomial(link = "logit"),
      data = mortgage_data)
```

ln(oddsaccepted) = b0 = b1 * 0.006724 + 1.484538 * employedTrue

```{r}
log_predictions <- tibble(
  tu_score = rep(seq(0, 710, 1), 2),
  employed = c(rep(TRUE, 711), rep(FALSE, 711))
) %>% 
  add_predictions(model = mortgage_model_2_terms, type = "response")

ggplot(mortgage_data) +
  geom_jitter(aes(x = tu_score, y = as.numeric(accepted)), alpha = 0.5, height = 0.1, width = 0.1) +
  geom_line(data = log_predictions, aes(x = tu_score, y = pred, colour = employed)) +
  labs(y = "Estimated p(Accepted)")

# can use our predictions by filtering our prediction table
log_predictions %>% 
  filter(tu_score == 600)
```
odds(employedTrue) / odds(employedFalse) = odds ratio

```{r}
odds_change(1.48, 1)
```

on average a customers odds of being accepted are 4.39x higher if they're employed

###model performance: building a binary classifier

i.e. assigns a class based on this predicted probability

if applicant's credit score is x and their employment is y, will we accpet them for a mortgage loan?

the probability level which we assign yes or no is called the threshold 

```{r}
mortgage_preds_2_terms <- mortgage_data %>% 
  add_predictions(mortgage_model_2_terms, type = "response") %>% 
  mutate(predicted_accepted = pred >= 0.6) #binary classifier
```
###model assessment - how often were we right (accepted = predicted_accepted)

confusion tool assessment matrix 

```{r}
library(janitor)
mortgage_preds_2_terms %>% 
  tabyl(accepted, predicted_accepted)
```

>task

```{r}
mortgage_3pred_model <- #creating 3 predictor model
  glm(accepted ~ tu_score + employed + age,
      family = binomial(link = "logit"),
      data = mortgage_data)

mortgage_data_with_3_pred <- mortgage_data %>% 
  add_predictions(mortgage_3pred_model) %>% 
  mutate(predicted_accepted = pred >= 0.6)

conf_mat <- mortgage_data_with_3_pred %>% 
  tabyl(accepted, predicted_accepted) %>% 
  adorn_title()
```
FALSE:FALSE & TRUE:TRUE are where your model is right

FALSE:TRUE & TRUE:FALSE are where your model is wrong 

True negative (701) | False positive (27)
False negative (102)| True negative (170)

>task

```{r}
mortgage_data_with_3_pred %>% 
  filter(tu_score == 594)

#false positive
#false positive
#true positive 
#true positive
#true positive
```

#single value for accuracy?

Accuracy: number of true pos. + number of true neg. / total
  - times we were right / total outcomes 
  
```{r}
(701+170) / 1000
```
we were right 87.1% of the time 

unfortunately accuracy doesn't react well to unbalanced data: so we use other measures:
  - rates (true positive rate, specificity, ...)
  - AUC
  - Gini 
  
```{r}
conf_mat

nTN = 701
nFP = 27
nFN = 102
nTP = 170

true_positive_rate = nTP / (nTP + nFN)

true_negative_rate = nTN / (nTN + nFP)

false_positive_rate = nFP / (nFP + nTN)

false_negative_rate = nFN / (nFN + nTP)
```
which to prioritise depends on the context 


